---
title: "AI in a Day Workshop: Baseline Survey — Item-by-Item Analysis"
author: "Prepared for the ESIIL workshop design team"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 2
    theme: flatly
    code_folding: hide
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE,
                      fig.width = 8.5, fig.height = 5)
library(dplyr)
library(tidyr)
library(ggplot2)
library(stringr)
library(forcats)
library(knitr)
library(kableExtra)
library(scales)

real_data <- TRUE   # FALSE → use de‑identified `broken-row‑survey‑data.csv`
if (real_data) {
  d <- read.csv(file.path("..", "data", "01_tidied-responses.csv"))
    #read.csv(file.path("data", "01_tidied-responses.csv"))
} else {
  d<- read.csv(file.path("data", "broken-row-survey-data.csv"))
}

# d   <- read.csv("broken-row-survey-data.csv", stringsAsFactors = FALSE)
key <- read.csv(file.path("..", "data", "01_question-lookup-table.csv"), stringsAsFactors = FALSE)

# Treat empty strings as item nonresponse
d[d == ""] <- NA
N <- nrow(d)

qtext <- function(v) key$question_text[match(v, key$name_in_data)]

theme_set(theme_minimal(base_size = 12) +
            theme(panel.grid.minor = element_blank(),
                  plot.title.position = "plot"))
fill_col <- "#2b7a78"

# ---- Helpers -----------------------------------------------------------------

# Frequency table + plot for a single-choice item
freq_tab <- function(var, lvls = NULL) {
  x <- d[[var]]
  n_ans <- sum(!is.na(x))
  tb <- tibble(Response = x) |>
    filter(!is.na(Response)) |>
    count(Response, name = "n") |>
    mutate(Percent = n / n_ans)
  if (!is.null(lvls)) {
    tb <- tb |> mutate(Response = factor(Response, levels = lvls)) |> arrange(Response)
  } else {
    tb <- tb |> arrange(desc(n))
  }
  attr(tb, "n_ans") <- n_ans
  tb
}

show_tab <- function(tb, caption = NULL) {
  n_ans <- attr(tb, "n_ans")
  tb |>
    mutate(Percent = percent(Percent, accuracy = 0.1)) |>
    kable(caption = caption) |>
    kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
    footnote(general = sprintf("Answered: %d of %d respondents (%s item nonresponse).",
                               n_ans, N, percent(1 - n_ans / N, accuracy = 1)),
             general_title = "")
}

bar_single <- function(tb, title, wrap = 40) {
  tb |>
    mutate(Response = str_wrap(as.character(Response), wrap),
           Response = factor(Response, levels = rev(str_wrap(as.character(tb$Response), wrap)))) |>
    ggplot(aes(x = Percent, y = Response)) +
    geom_col(fill = fill_col) +
    geom_text(aes(label = percent(Percent, accuracy = 1)), hjust = -0.15, size = 3.4) +
    scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.12))) +
    labs(title = str_wrap(title, 85),
         subtitle = sprintf("n = %d respondents answering", attr(tb, "n_ans")),
         x = "Percent of respondents answering", y = NULL)
}

# Multi-select items: options are concatenated with commas, but many option
# texts themselves contain commas. We therefore match full canonical option
# strings (longest first, removing each match so no option can double-count
# as a substring of another). The residual check below verifies that every
# response string is fully accounted for by the canonical lists.
count_multiselect <- function(var, options) {
  x <- d[[var]]
  x <- x[!is.na(x)]
  n_ans <- length(x)
  ord <- order(-nchar(options))
  counts <- integer(length(options))
  resid <- x
  for (j in ord) {
    found <- grepl(options[j], resid, fixed = TRUE)
    counts[j] <- sum(found)
    resid[found] <- sub(options[j], "", resid[found], fixed = TRUE)
  }
  leftover <- gsub("[, ]", "", resid)
  tb <- tibble(Option = options, n = counts, Percent = counts / n_ans) |>
    arrange(desc(n))
  attr(tb, "n_ans") <- n_ans
  attr(tb, "unmatched") <- sum(leftover != "")
  tb
}

show_ms <- function(tb, caption = NULL) {
  stopifnot(attr(tb, "unmatched") == 0)  # every response fully parsed
  n_ans <- attr(tb, "n_ans")
  tb |>
    mutate(Percent = percent(Percent, accuracy = 0.1)) |>
    kable(caption = caption) |>
    kable_styling(bootstrap_options = c("striped", "condensed"), full_width = FALSE) |>
    footnote(general = sprintf(
      "Select-all-that-apply; percentages are of the %d respondents answering this item (%d of %d skipped it).",
      n_ans, N - n_ans, N), general_title = "")
}

bar_ms <- function(tb, title, wrap = 55) {
  tb |>
    mutate(Option = str_wrap(Option, wrap),
           Option = fct_reorder(Option, n)) |>
    ggplot(aes(x = Percent, y = Option)) +
    geom_col(fill = fill_col) +
    geom_text(aes(label = percent(Percent, accuracy = 1)), hjust = -0.15, size = 3.2) +
    scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.12))) +
    labs(title = str_wrap(title, 85),
         subtitle = sprintf("Select all that apply; n = %d respondents answering", attr(tb, "n_ans")),
         x = "Percent selecting", y = NULL)
}
```

```{r option-lists, include=FALSE}
opts <- list(
  AIUse_reasons = c(
    "My institution’s policies",
    "Desire to improve the quality of my work",
    "Desire to work more efficiently",
    "Expand the scope of information and resources that are accessible to me (e.g., learning a new coding language, entering a new sub-discipline)",
    "Get personalized assistance for work challenges",
    "Financial cost",
    "Worried about the perceived loss of integrity by my peers or institution",
    "Worried about allegations of plagiarism or copyright infringement",
    "The environmental impact of GenAI infrastructure (e.g., water use, electricity use, carbon emissions)",
    "Security concerns (e.g. prompt injection, file deletion, agentic access to private data, tokens or passwords)",
    "Anxiety that using GenAI will inhibit my own learning or skill acquisition",
    "Lack of protection for my data privacy",
    "Concerns regarding false results / hallucinations",
    "Concerns regarding biased algorithmic results",
    "Other"
  ),
  Task_interest = c(
    "For literature review",
    "To summarize a relevant article",
    "To suggest ideas for research",
    "To validate my approach or methods",
    "To structure my thoughts (e.g., outlining text, reformatting notes)",
    "To generate text, which I then edit before incorporating into publishable written work",
    "To generate administrative text (e.g., emails, meeting notes)",
    "To provide feedback and edit my written work",
    "To access and understand research materials not in my native language",
    "To improve my understanding of a new topic",
    "To quality control data",
    "To generate code",
    "To review code",
    "To reorganize, refactor, add comments, or tidy existing code",
    "For statistical analysis",
    "To generate images, video, music, or other media",
    "For general workplace productivity (e.g., administrative tasks)",
    "To generate research data (e.g. computer vision, image or acoustic analysis, natural language processing)",
    "Other"
  ),
  TechSkill_Interest = c(
    "Responsible use of GenAI",
    "Using a specialized AI coding assistant such as Codex or Claude Code",
    "Run a model locally on a personal computer",
    "Use open-source models",
    "Use GenAI agents that can complete multi-step tasks",
    "Run models on institutional or cloud computing resources",
    "Develop AI-powered applications or tools",
    "Create custom GPTs, projects, or assistants",
    "Fine-tune or customize GenAI models",
    "Prompt Engineering",
    "Use GenAI tools to connect to external databases",
    "Use GenAI through an API (e.g., accessing Gemini via its API through your IDE of choice)",
    "Write scripts that call GenAI models programmatically",
    "Connect GenAI tools to external software",
    "Build Retrieval-Augmented Generation (RAG) systems",
    "Not sure",
    "Other"
  ),
  Training = c(
    "Self-teaching through short-form online websites / videos (i.e., minutes of content)",
    "Self-teaching through long-form online websites / videos (i.e., hours of content)",
    "Through colleagues or peers",
    "Through social media",
    "Synchronous virtual workshops (~1-8 hours)",
    "In-person workshops (~1-8 hours)",
    "Multi-day short courses",
    "Formal coursework (e.g., semester/quarter)",
    "Other"
  ),
  PromisingOpps = c(
    "Automating repetitive manual processes",
    "Analyzing large or complex datasets (including qualitative text data)",
    "Offloading administrative burdens and mundane office tasks",
    "Creating new research tools/software",
    "Accelerating scientific research progress and breakthrough speeds",
    "Real-time data analytics and dynamic visualization",
    "Improving data governance and cataloging",
    "Generating insights for data-informed decision-making",
    "Democratizing data and data insights for broader access",
    "Aiding course design and educational curriculum development",
    "Developing new, highly specialized ecological models",
    "Evaluating academic or student work",
    "Beneficial job transformation",
    "None (No opportunities associated with using GenAI for research and learning)",
    "Other"
  ),
  Challenges = c(
    "Lack of transparency from service providers (e.g., data privacy concerns)",
    "The extreme gravity/severity of the risks associated with GenAI",
    "The high number of individual risks associated with GenAI",
    "The rapid pace of GenAI change and development",
    "Lack of clear industry best practices",
    "Conflicting opinions on GenAI usage",
    "Insufficient institutional governance or clear rules",
    "Unauthorized or unvetted stakeholder/student use",
    "Lack of time to learn new AI-prompting or tool skills",
    "Lack of technical GenAI expertise",
    "Lack of financial budget to secure premium GenAI services",
    "Inadequate procurement and IT security clearing processes",
    "Lack of leadership support at my institution",
    "Lack of access to sufficient computing resources",
    "No challenges associated with using AI",
    "Other"
  ),
  Prof_Role = c(
    "Researcher",
    "Educator / Instructor",
    "Student",
    "Data Professional (e.g., Data Scientist, Information Manager)",
    "Project Manager",
    "Administrator",
    "Policy Expert or Advocate",
    "Other"
  ),
  Race_Ethnicity = c(
    "White / Caucasian",
    "Asian or Asian American",
    "Hispanic, Latino/a/x, or Spanish Origin",
    "Black or African American",
    "American Indian or Alaska Native",
    "Native Hawaiian or Other Pacific Islander",
    "Prefer not to answer",
    "Other"
  )
)
```

# Executive summary: takeaways for workshop design

```{r summary-stats, include=FALSE}
use_tb  <- freq_tab("AIUse_Freq", c("Never","Yearly","Monthly","Weekly","Daily"))
att_tb  <- freq_tab("Gen_Attitude")
task_tb <- count_multiselect("Task_interest", opts$Task_interest)
tech_tb <- count_multiselect("TechSkill_Interest", opts$TechSkill_Interest)
des_tb  <- count_multiselect("Training_Desired", opts$Training)
rec_tb  <- count_multiselect("Training_Received", opts$Training)
rsn_tb  <- count_multiselect("AIUse_reasons", opts$AIUse_reasons)
chal_tb <- count_multiselect("Challenges", opts$Challenges)

pct_of <- function(tb, lvl) {
  col <- if ("Response" %in% names(tb)) tb$Response else tb$Option
  percent(tb$Percent[match(lvl, col)], accuracy = 1)
}
```

Of the **`r N` survey respondents**, most are researchers in academia (ecology and
environmental science especially), highly educated, and regular users of data
science tools. Eight takeaways stand out for the design of an AI in a Day workshop:

1. **The audience is experienced but polarized in AI use.** About 60% of
   those answering already use GenAI weekly or daily, yet roughly 1 in 5 report
   *never* using it. Plan tiered or parallel activities so daily users and
   never-users both get value; a one-speed curriculum will lose one end of the room.

2. **Skepticism is the dominant stance, and a quarter are opposed outright.**
   The modal attitude is "a mix of caution and enthusiasm," and "Opposed to
   GenAI" is the second most common response. This is not an audience to
   evangelize to. Frame the day around critical, evidence-based engagement:
   what these tools do well, where they fail, and how to verify their output.

3. **Environmental impact is the single most-cited factor affecting use** (74%
   of those answering), ahead of hallucinations (69%) and worry that AI use
   will inhibit one's own learning (63%). For environmental scientists this is
   a values issue as much as a practical one. Address it directly with content
   on the actual energy/water footprint of inference vs. training, and connect
   it to the strong expressed interest in local and open-source models.

4. **Code-centric tasks top the learning agenda.** Reviewing code (63%) and
   generating code (62%) are the most-wanted task applications, followed by
   refactoring/tidying code, learning new topics, and general productivity.
   Hands-on coding-assistant exercises should anchor the day, with statistical
   analysis and literature-review use cases as secondary threads.

5. **"Responsible use of GenAI" is the #1 technical skill interest** (52%),
   ahead of any specific tool skill. Weave verification, citation, privacy,
   and disclosure practices through every hands-on module rather than
   quarantining ethics in a single closing slot.

6. **Prior training is almost entirely informal.** Two-thirds of those who
   report any training got it from short videos or from colleagues; formal
   coursework and multi-day courses are rare. Assume no shared vocabulary or
   mental model of how LLMs work, even among daily users.

7. **The chosen format matches demand.** Synchronous workshops of ~1–8 hours
   are the most desired training format (virtual 60%, in-person 42% of those
   answering), exactly the "AI in a Day" footprint. Pair the day with
   short-form follow-up materials, the self-teaching mode most participants
   already use.

8. **Institutional context is mostly permissive, and Gemini is the common
   denominator.** Where policies exist they lean supportive, and the most
   frequently named institutionally provided tools are Gemini, ChatGPT/ChatGPT
   Edu, and Copilot. Demos built on widely available tools (or free/open
   models) will travel better than ones requiring paid subscriptions.

**A caution on generalization:** respondents skew heavily academic (79% higher
ed), doctorally trained, and self-selected into a survey about AI. Attitude and
interest profiles for the broader target audience may differ.

# Data notes

- The data file contains **`r N` rows** and no direct identifiers; the ID column
  is `fake_row` (values 1–`r N`, in order).
- Empty cells are treated as item nonresponse. Nonresponse grows over the course
  of the survey (see funnel below), consistent with attrition, so percentages
  in this report use **respondents answering each item** as the denominator,
  with the item n shown on every table and figure.
- Two items in the question lookup table (`AI_tools`, and the three open-ended
  learning-outcome items `LOs_1`–`LOs_3`) do not appear in the response file,
  so they are not analyzed here.
- Multi-select ("select all that apply") responses are stored as comma-joined
  strings in which many option texts themselves contain commas. Options were
  counted by exact full-string matching against the canonical option lists, and
  a residual check confirms every response string is fully accounted for.

```{r funnel, fig.height=6}
main_items <- c("AIUse_Freq","AIUse_reasons","Task_interest","TechSkill_Interest",
                "Training_Received","Training_Desired","Gen_Attitude","PromisingOpps",
                "Challenges","Policies","Career_Stage","Prof_Role","Work_Sector",
                "Formal_Ed","Field","DS_Freq","GenAI_Resources","Gender","LGBTQIA",
                "Race_Ethnicity","Neurodiverse","Caregiver","FirstGen")
tibble(item = factor(main_items, levels = rev(main_items)),
       answered = sapply(main_items, function(v) sum(!is.na(d[[v]])))) |>
  ggplot(aes(x = answered, y = item)) +
  geom_col(fill = fill_col) +
  geom_text(aes(label = answered), hjust = -0.2, size = 3.2) +
  scale_x_continuous(expand = expansion(mult = c(0, 0.1))) +
  labs(title = "Respondents answering each item (survey order, top to bottom)",
       subtitle = sprintf("Total rows in file: %d", N),
       x = "Respondents answering", y = NULL)
```

Note that the two items with the lowest response counts, `Training_Received`
(n = `r sum(!is.na(d$Training_Received))`) and `GenAI_Resources`
(n = `r sum(!is.na(d$GenAI_Resources))`), are also items where "none" may
simply have been left blank, so their percentages deserve extra caution.

# Who responded

## Professional role

*`r qtext("Prof_Role")`*

```{r prof-role}
tb <- count_multiselect("Prof_Role", opts$Prof_Role)
show_ms(tb)
bar_ms(tb, "Primary professional role or identity")
```

## Career stage

*`r qtext("Career_Stage")`*

```{r career}
lv <- c("Preparation Stage (Currently pursuing a graduate degree)",
        "Early Career Stage (1–9 years of experience post-degree)",
        "Mid-Career Stage (10–25 years of experience)",
        "Mature Career Stage (26+ years of experience)")
tb <- freq_tab("Career_Stage", lv)
show_tab(tb)
bar_single(tb, "Career stage")
```

## Work sector

*`r qtext("Work_Sector")`*

```{r sector}
tb <- freq_tab("Work_Sector")
show_tab(tb)
bar_single(tb, "Main work sector")
```

## Formal education

*`r qtext("Formal_Ed")`*

```{r formal-ed}
lv <- c("4-year undergraduate degree (B.S., B.A., etc.)",
        "Master’s degree (M.S., M.A., etc.)",
        "Doctoral degree (Ph.D., Sc.D., etc.)", "Other")
tb <- freq_tab("Formal_Ed", lv)
show_tab(tb)
bar_single(tb, "Highest level of formal education")
```

## Primary field or discipline

*`r qtext("Field")`*

```{r field}
tb <- freq_tab("Field")
show_tab(tb)
bar_single(tb, "Primary field or discipline")
```

## Data science frequency

*`r qtext("DS_Freq")`*

```{r ds-freq}
lv <- c("I do not use data science in my research/role",
        "Yearly", "Monthly", "Weekly", "Daily")
tb <- freq_tab("DS_Freq", lv)
show_tab(tb)
bar_single(tb, "Frequency of data science use in primary role")
```

Roughly `r percent(sum(tb$Percent[tb$Response %in% c("Weekly","Daily")]), accuracy = 1)`
of those answering use data science weekly or daily. This is a technically
fluent audience; hands-on coding content is viable for most of the room.

# Current GenAI use and attitudes

## Frequency of GenAI use

*`r qtext("AIUse_Freq")`*

```{r aiuse-freq}
show_tab(use_tb)
bar_single(use_tb, "How often do you use GenAI tools in your work?")
```

Use is strikingly bimodal:
`r percent(sum(use_tb$Percent[use_tb$Response %in% c("Weekly","Daily")]), accuracy = 1)`
use GenAI at least weekly while `r pct_of(use_tb, "Never")` never use it at all.

## Reasons affecting likelihood of use

*`r qtext("AIUse_reasons")`*

This item mixes motivators (efficiency, quality) and deterrents (environmental
impact, hallucinations) in one list, so it is best read as "which considerations
are on respondents' minds."

```{r reasons, fig.height=7}
show_ms(rsn_tb)
bar_ms(rsn_tb, "Considerations affecting likelihood of using GenAI for work")
```

The four most-selected considerations are all concerns rather than motivations.
Environmental impact leads at `r percent(rsn_tb$Percent[1], accuracy = 1)`.

## General attitude toward GenAI

*`r qtext("Gen_Attitude")`*

```{r attitude}
lv <- c("Opposed to GenAI", "Cautious", "A mix of caution and enthusiasm",
        "Indifferent", "Enthusiastic", "Very enthusiastic", "Other")
tb <- freq_tab("Gen_Attitude", lv)
show_tab(tb)
bar_single(tb, "General attitude toward GenAI")
```

## Attitude by frequency of use

```{r att-by-use, fig.height=5.5}
att_lv <- c("Opposed to GenAI", "Cautious", "A mix of caution and enthusiasm",
            "Indifferent", "Enthusiastic", "Very enthusiastic", "Other")
d |>
  filter(!is.na(AIUse_Freq), !is.na(Gen_Attitude)) |>
  mutate(AIUse_Freq = factor(AIUse_Freq, c("Never","Yearly","Monthly","Weekly","Daily")),
         Gen_Attitude = factor(Gen_Attitude, att_lv)) |>
  count(AIUse_Freq, Gen_Attitude) |>
  group_by(AIUse_Freq) |>
  mutate(p = n / sum(n), n_grp = sum(n)) |>
  ungroup() |>
  ggplot(aes(x = AIUse_Freq, y = p, fill = fct_rev(Gen_Attitude))) +
  geom_col(width = 0.75) +
  scale_y_continuous(labels = percent_format()) +
  scale_fill_brewer(palette = "RdYlBu", direction = -1, name = "Attitude") +
  labs(title = "Attitude toward GenAI, by frequency of use",
       subtitle = "Column percentages within each use-frequency group",
       x = "Frequency of GenAI use", y = "Percent within group")
```

Attitude and use go hand in hand, but caution persists even among frequent
users; treat "already uses AI daily" and "is sold on AI" as different things.

## Institutional policies

*`r qtext("Policies")`*

```{r policies}
lv <- c("Very restrictive/opposed", "Somewhat restrictive/opposed", "Neutral",
        "Somewhat permissive/supportive", "Very permissive/supportive",
        "There are not any policies or guidelines at my institution", "Other")
tb <- freq_tab("Policies", lv)
show_tab(tb)
bar_single(tb, "Orientation of institutional GenAI policies and guidelines")
```

## GenAI resources available through the institution (open text)

*`r qtext("GenAI_Resources")`*

```{r resources}
x <- tolower(d$GenAI_Resources[!is.na(d$GenAI_Resources)])
n_ans <- length(x)
kw <- c(Gemini = "gemini", `ChatGPT (incl. ChatGPT Edu)` = "chatgpt|gpt edu",
        Copilot = "copilot", Claude = "claude", NotebookLM = "notebooklm",
        Perplexity = "perplexity", `Llama / open models` = "llama|open.?source",
        `None mentioned` = "^\\s*none|no resources|nothing",
        `Not sure / unaware` = "not sure|unsure|don't know|dont know|no idea|unaware")
tb <- tibble(Option = names(kw),
             n = sapply(kw, function(p) sum(grepl(p, x))),
             Percent = n / n_ans) |>
  arrange(desc(n))
attr(tb, "n_ans") <- n_ans; attr(tb, "unmatched") <- 0
show_ms(tb, caption = "Keyword mentions in open-text responses")
bar_ms(tb, "Institutionally available GenAI resources (keyword mentions)")
```

Open-text mentions, so categories overlap and absence of a mention does not
imply absence of the resource. Gemini is by far the most commonly named
institutional resource.

# What they want to learn

## Tasks of interest

*`r qtext("Task_interest")`*

```{r tasks, fig.height=8}
show_ms(task_tb)
bar_ms(task_tb, "Tasks respondents want to learn to use GenAI for")
```

## Technical skills of interest

*`r qtext("TechSkill_Interest")`*

```{r techskills, fig.height=7}
show_ms(tech_tb)
bar_ms(tech_tb, "Technical skills respondents want to learn")
```

## Training already received

*`r qtext("Training_Received")`*

```{r trainrec}
show_ms(rec_tb)
bar_ms(rec_tb, "Formats of GenAI training already received")
```

Only `r sum(!is.na(d$Training_Received))` of `r N` respondents reported any
training at all, and what exists is dominated by informal self-teaching and
peer learning.

## Training desired

*`r qtext("Training_Desired")`*

```{r traindes}
show_ms(des_tb)
bar_ms(des_tb, "Formats of GenAI training desired")
```

```{r train-compare, fig.height=5.5}
bind_rows(rec_tb |> mutate(which = "Received"),
          des_tb |> mutate(which = "Desired")) |>
  mutate(Option = str_wrap(Option, 45)) |>
  mutate(Option = fct_reorder(Option, Percent, .fun = max)) |>
  ggplot(aes(x = Percent, y = Option, fill = which)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  scale_x_continuous(labels = percent_format(), expand = expansion(mult = c(0, 0.08))) +
  scale_fill_manual(values = c(Received = "grey70", Desired = fill_col), name = NULL) +
  labs(title = "Training received vs. training desired, by format",
       subtitle = sprintf("Percent of respondents answering each item (received n = %d, desired n = %d)",
                          attr(rec_tb, "n_ans"), attr(des_tb, "n_ans")),
       x = "Percent selecting", y = NULL)
```

The gap between received and desired training is largest for structured,
synchronous formats (virtual and in-person workshops, multi-day courses),
while social media is the one format people have used more than they want.

# Opportunities and challenges

## Most promising opportunities

*`r qtext("PromisingOpps")`*

```{r opps, fig.height=7}
tb <- count_multiselect("PromisingOpps", opts$PromisingOpps)
show_ms(tb)
bar_ms(tb, "Most promising opportunities for GenAI in research and learning")
```

Note that `r percent(tb$Percent[tb$Option == "None (No opportunities associated with using GenAI for research and learning)"], accuracy = 1)`
selected "None," consistent with the sizable opposed group on the attitude item.

## Most difficult challenges

*`r qtext("Challenges")`*

```{r challenges, fig.height=7}
show_ms(chal_tb)
bar_ms(chal_tb, "Most difficult challenges for GenAI in research and learning")
```

# Demographics

## Gender

*`r qtext("Gender")`*

```{r gender}
tb <- freq_tab("Gender")
show_tab(tb)
bar_single(tb, "Gender identity")
```

## LGBTQIA+ identification

*`r qtext("LGBTQIA")`*

```{r lgbtq}
tb <- freq_tab("LGBTQIA")
show_tab(tb)
```

## Race and ethnicity

*`r qtext("Race_Ethnicity")`*

```{r race}
tb <- count_multiselect("Race_Ethnicity", opts$Race_Ethnicity)
show_ms(tb)
bar_ms(tb, "Racial or ethnic identification (select all that apply)")
```

## Neurodivergence, caregiving, and first-generation status

```{r other-demo}
tb <- freq_tab("Neurodiverse")
show_tab(tb, caption = qtext("Neurodiverse"))

lv <- c("Not a caregiver", "Caregiver in the past, but not currently",
        "Contributor/Secondary caregiver",
        "Share caregiving responsibilities equally with another person",
        "Primary caregiver", "Prefer not to answer")
tb <- freq_tab("Caregiver", lv)
show_tab(tb, caption = qtext("Caregiver"))

tb <- freq_tab("FirstGen")
show_tab(tb, caption = qtext("FirstGen"))
```

About one in three of those answering identify as a current caregiver of some
kind, and about one in four identify as neurodivergent or as having a
significant sensory or mobility challenge. Both argue for accessible pacing,
recordings or asynchronous follow-ups, and breaks in a day-long format.
